A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2024-01-05 main.tex
boilerplate about preprint

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

@@

>>>>

\date{Accepted: 10 December 2023}
% The correct dates will be entered by the editor

@@

\vspace*{1em}
\paragraph{Preprint.} This preprint has not undergone peer review (when applicable) or any
post-submission improvements or corrections. The Version of Record of
this article is published in \emph{Empirical Software Engineering}, and is available
online at \url{https://doi.org/10.1007/s10664-023-10437-1}.

To our knowledge, the publisher has not contributed any post-submission improvements or corrections, aside from some edits that we reverted.
